Incorporating Gyroscope Information in Gesture Recognition

### 2011-12-17 paper/paper.tex
fixed typos in conclusion
more changes

\documentclass[12pt]{article}
\usepackage[margin=1.0in]{geometry}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{indentfirst}

@@

@@

\begin{figure}
\center
\includegraphics[scale=0.5]{accuracy_vs_num_clusters.png}
\caption{Classification accuracy of Cluster-Matching-HMM for 6 gestures}
\label{fig:alphabetsize}
\end{figure}

>>>>

\documentclass[11pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{indentfirst}
\usepackage{wrapfig}

@@

We tested our algorithms on six datasets: circles (with the phone held relatively flat), triangles (with the phone held similarly), bowling motions, flicking the phone upward, and flicking up and to the right.  The last set, used only in a few tests, consisted of squares.  These datasets all include gestures of deliberately variable quality: some are carefully controlled, and others less so.

@@

\begin{wrapfigure}{r}{0.5\textwidth}
\center
\includegraphics[scale=0.5]{accuracy_vs_num_clusters.png}
\caption{Classification accuracy of Cluster-Matching-HMM for 6 gestures}
\label{fig:alphabetsize}
\end{wrapfigure}
